---
title: "Check for Duplicate Subjects in Data"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In large data collection efforts it is not uncommon that subject ID's will occasionally get entered incorrectly when adminstering a task, or a subject is wrongly adminstered the task multiple times. The `duplicates_check()` function will check for duplicate subject ID's, remove them, and save them to a file so you can sort them out later. 

Identifying these duplicates and making decisions on what to do with them should be done before any data processing is done. Here is a template script that can be used to check for duplicates and save them to a file so that you can make decisions on how to handle them. 

```{r eval=FALSE}
# run this script to check for duplicates
library(stringr)
library(readxl)
library(purrr)
library(psyworkflow)

extract_name <- function(path) {
  str_extract(path, "regex to extract task name")
}

files_import <- list.files(path = "folder location to raw data", 
                           pattern = "survey", 
                           recursive = TRUE, full.names = TRUE)

files_import |>
  map(\(file) {
    name <- extract_name(file)
    read_excel(file) |>
      duplicates_check(unique_id = "subject",
                       date_time = c("date", "time"),
                       remove = FALSE,
                       keep_by = "least missing",
                       save_as = 
                         paste0("folder location to raw data/duplicates/", 
                                name, ".csv"))
  })

```

