# STUDYNAME

1 - 2 sentence description.

## Directory Organization

------------------------------------------------------------------------

-   **data**: All data files are stored here

    -   **raw**: raw data files for each task

    -   **scored**: scored data files for each task

    -   **logs**: logs for data cleaning procedures

    -   Demographics.csv: demographics data file

-   **documents**: Any documents related to the study and analysis procedure

-   **R**: All R scripts used for processing and analyzing data

-   **results**: All result output files from data analysis scripts

-   **tasks**: Experimental programs for all the tasks used in the study

## Required Packages

------------------------------------------------------------------------

```{r eval = FALSE}
source("R/_required_packages.R")
```

## Data Preparation

------------------------------------------------------------------------

Create tidy raw data files from messy raw data files

-   **Import Directory**: data/raw/messy

-   **Output Directory**: data/raw

```{r}
source("R/0_task_raw.csv")

rm(list=ls())
```

## Data Scoring and Cleaning

------------------------------------------------------------------------

Create scored and cleaned data files from raw data files

-   **Import Directory**: data/raw

-   **Output Directory**: data/scored

-   **Data Cleaning**: A log of which subjects were removed for each task due to data cleaning can be found in data/**logs**

    [provide a general description of some data cleaning decisions]

-   **Reliability**: [provide a general description of how reliability was calculated]

```{r}
library(rmarkdown)
render("R/1_task_score.R", output_dir = "data/logs")

rm(list=ls())
```

Create merged data file from scored data files

**Import Directory**: data/scored

**Merged File**: data/**Data.csv**

```{r}
source("R/2_merge.R", echo = TRUE)

rm(list=ls())
```

## Statistical Analysis and Data Visualization

------------------------------------------------------------------------

Perform statistical analysis and data visualization

Output is saved as **.html** files to **results/**

```{r}
rmarkdown::render("R/3_MainAnalysis.Rmd",
                  output_dir = "results", 
                  output_file = "MainAnalysis.html")

rm(list=ls())
```
